LHC abort gap monitor electronics upgrade

### 2024-04-24 bibliography.tex
added new bibtexs and working principle finished
updated old system und new system daq chapters

        % https://cds.cern.ch/record/1272172/files/CERN-BE-2010-026.pdf
        \bibitem{bsra_operation}Bart Pedersen, S., Lefevre, T., Bravin, E., Boccardi, A.,
            Goldblatt, A., Jeff, A., Roncarolo, F. \& Fisher, A. \emph{First Operation of
            the Abort Gap Monitors for LHC}.  (2010,5), \url{http://cds.cern.ch/record/1272172}

        \bibitem{Fisher_bsra}Fisher, A. \emph{Expected Performance of the LHC
            Synchrotron-Light Telescope (BSRT) and Abort-Gap Monitor (BSRA).}
            (CERN,2010), \url{https://cds.cern.ch/record/1261191}

        % https://cds.cern.ch/record/2295107/files/1638883_171-176.pdf
        \bibitem{machine_protect}Bravin, E., Belohrad, D., Calvo, E. \& Mazzoni, S. Beam
            instrumentation for machine protection.  (2014), \url{https://cds.cern.ch/record/2295107}

        % https://cds.cern.ch/record/1261191/files/performance-note-014.pdf
        \bibitem{expected_performance_bsrt}Fisher, A. Expected Performance of the LHC
            Synchrotron-Light Telescope (BSRT) and Abort-Gap Monitor (BSRA).
            (CERN, 2010, 3), \url{https://cds.cern.ch/record/1261191}

        \bibitem{abort_gap_monitor_thesis}Pacner, P. LHC Abort Gap Monitor
            Acquisition System, Master thesis, (Brno, 2022, 59)

>>>>

        \bibitem{high_sensitivity_measurement} C. Fischer, \emph{High Sensitivity
            Measurement of the Beam Longitudinal Distribution of the LHC Beams}, 
            (2003,1), LHC-BP-ES-0005, rev. 2.0,
            \url{https://edms.cern.ch/document/328145/2.0}

        \bibitem{bsra_first_operation}Bart Pedersen, S., Lefevre, T., Bravin, E., Boccardi, A.,
          Goldblatt, A., Jeff, A., Roncarolo, F. \& Fisher, A. \emph{First Operation of
          the Abort Gap Monitors for LHC}.  (2010,5), \url{http://cds.cern.ch/record/1272172}

        \bibitem{lhcb_asic} Böhner, G., Falvard, A., Lecoq, J., Perret, P. \& Trouilleau,
            C. \emph{Very front-end electronics for the LHCb preshower}.  (CERN,2000,10),
            \url{http://cds.cern.ch/record/691512}

        \bibitem{my_thesis}Pacner, P. LHC Abort Gap Monitor
            Acquisition System, Master thesis, (Brno, 2022, 59)

        % \bibitem{Fisher_bsra}Fisher, A. \emph{Expected Performance of the LHC
        %     Synchrotron-Light Telescope (BSRT) and Abort-Gap Monitor (BSRA).}
        %     (CERN,2010), \url{https://cds.cern.ch/record/1261191}

        % % https://cds.cern.ch/record/2295107/files/1638883_171-176.pdf
        % \bibitem{machine_protect}Bravin, E., Belohrad, D., Calvo, E. \& Mazzoni, S. Beam
        %     instrumentation for machine protection.  (2014), \url{https://cds.cern.ch/record/2295107}

### 2024-04-24 paper.tex
updated old system und new system daq chapters

\section{System architecture}
The system comprises three main parts. The first part is the optical front-end
(OF), which includes a preamplifier positioned beneath the vacuum chamber. The
second part is a data acquisition system (DAQ) deployed on an FPGA platform
located outside the radiation area. The third part involves software (SW) that
retrieves, interprets, and presents the measured data, facilitating interaction
with the instrument. The system architecture is illustrated in
Fig.~\ref{fig:bsra_chain}, with each part labeled accordingly.
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{bsra_chain.pdf}
    \caption{BSRA Chain}
    \label{fig:bsra_chain}
\end{figure} 
The diagram on the left depicts the layout of the LHC, with beam 1 represented
in red and beam 2 in blue. It includes all four experiments (Alice, Atlas,
LHCb, and CMS). The AGM is situated at Point 4 (indicated by the yellow
square), close to the CMS experiment. The Timing, Trigger, and Control system
(TTC) is shown as a purple rectangle in the center of the LHC ring. This system
receives RF clocking and broadcasts it as messages on the network (TTC
distribution)~\cite{ttc_distribution}. The AGM extracts bunch clock information
(corresponding to the position of bunches) and turn clock information (marking
the start of a turn) from these messages.\\
Beam intensity is gathered by measuring the synchrotron light (SL), as
indicated by the red arrow directed towards the Multi-channel photomultiplier
(MCP-PMT). The light reaches the MCP-PMT in the optical front-end (OF).
Subsequently, the signal is transmitted over a \SI{100}{m} cable. To compensate
for losses in the cable, the signal is amplified beforehand. It then proceeds
to the Data Acquisition (DAQ) system, which measures \SI{6.4}{\micro\second}
window and integrates the intervals of \SI{100}{\nano\second}. This creates set
of 64 values published to the SW every \SI{10}{\micro\second}.

\subsection{Working principle}

The measurement period is determined by the MCP-PMT used, which is the gated
HAMAMATSU R5916U-50 with a duty cycle of \SI{1}{\%}. With a gate pulse duration
of \SI{3}{\micro\second} and one turn cycle length of \SI{89}{\micro\second},
measurements are taken every 4th clock cycle (\SI{356}{\micro\second}),
reducing the duty cycle to \SI{0.84}{\%}.\\
The system captures 64 values with a granularity of \SI{100}{\nano\second}. The
MCP-PMT gate duration is \SI{3}{\micro\second} providing an additional degree of
freedom in system control. The data undergo exponential moving
averaging and are provided to the software every \SI{100}{\micro\second}. Due to
variatous particle effects, the time taken to populate the AG ranges from
\SI{1.6}{\second} to \SI{25}{\second}~\cite{high_sensitivity_measurement}.

\subsection{Current Solution}
The System is placed at the point 4 sharing the optical line with the BSRT
[REF]. It converts incoming light through MCP-PMT HAMAMATSU R5916U-50 into
electric current. The current is converted to voltage by transimpedance
amplifier HAMAMATSU C5594 with static gain \SI{36}{dBV}, bandwith \SI{1.5}{GHz}
and the low cutoff frequency 50kHz.
The amplified signal is send to the switching analog integrators inside ASIC
lhcb2002b mounted to the IBMS FMC card. The card is connected to the DAB64x
deploying FPGA Altera Stratix EP1S400. 
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{existing_system_processing.pdf}
    \caption{Current system block diagram}
    \label{fig:current_system_processing}
\end{figure}
The current system schematic is in Fig.~\ref{fig:current_system_processing}. It
uses preintegration in the analog integrators behind the pre-amplifier. One
outputs a value while the other one is measuring every \SI{25}{ns}. Inside the
gateware the samples are summed to get 100ns integrals. Each analog integrator
has different gain, offset and is not temperature invariant. Therefore
different coefficients are applied at this stage as well. 
The system provides the two sets of data. It measures the evolution of average
and standard deviation. The 2 x 64 values are stored in the Block RAM and
fetched by the PC with running FESA server.

\subsection{Constraints and Limitations}
The system bottle neck is the analog integration. There is one installation per
beam each having IBMS with different gain, offset, correction coefficients and
40 MHz ADCs. When the IBMS is replaced, it needs to be recalibrated. The ASIC
has not deterministic time stamps, so dead-times lengths do not match. This is
causing artefacts at the opening and closing of the gate in the output plot.
The dynamic range can be controled by the optical filters not via amplifier,
because of static gain. Finally the DAB64x is obsolate platform, which
complicates its maintenance.

\section{System Upgrade}
The motivation to create a new Abort Gap Monitor is initiated by the problems
associated with the analog integrators in lhcb2002b. These cause measurements
errors and make the AGM difficult to calibrate[REF]. And the second driver to
redesign the system was the platform obsolance reducing simplicity of
maintenance. \\ 
As a platform the new VFC-HD Carrier is used with additional RTM board
providing driver for the gate and control of the built-in test LED. The last
major change was of the shelf 500MSPS 14-bit ADC reducing the maintanence
efford.

\subsection{Low band Amplifier}
The amplifier installed close to the MCP-PMT was custom designed. The purpose
is different light intensity of ion and proton beams to obtain higher dynamic
range. \\ 
% A = U^2/(i^2 * R^2) => A_dB = 20*log10(U/(i*R))
In the Fig. \ref{fig:amp_schematics} is shown amplifier's block scheme. All the
settings is controlled via UART interface. It provides changing the variable
current-to-voltage conversion factor from \SI{5.8}{mV/\micro A} -
\SI{1.1}{V/\micro A}. This corresponds to the Voltage gain from \SI{41}{dB} to
\SI{87}{dB}. The ADC has a no zero offset, so the signal can be shifted in the
amplifier before post-processing.\\
The amplifier features also alarm signal generator. This serves to turn of the
gate, when the light impinging is to intense and it could damage the
multi-channel plate inside the PMT. The alarm signal is send to the gateware,
where it is handled. The alarm feature has a variable threshold set.   
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{amp_schematics.pdf}
    \caption{upgraded amplifier}
    \label{fig:amp_schematics}
\end{figure}
The amplifier design has three switches. First switch can set pre-integrator,
to filter out spikes caused by dark counts of the PMT. Second switch can
activate either manual or gate driven integration of the acquisition window.  
Last switch activates low pass filtering with cutoff frequency of 40MHz.

\subsection{Acquisition system}
The DAQ was completly redesigned, because of the new platform and additional HW
components. The Fig. \ref{fig:bsra_daq} shows, how the signal is processed an
published from the DAQ.
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{bsra_daq.pdf}
    \caption{Ackquisition system schematics}
    \label{fig:bsra_daq}
\end{figure}
The ADC takes amplified data from MCP-PMT and samples them with 500MSPS
asynchronously to the LHC timing. To calculate the integrals, the system tags
each of the sample. This is done, that tagging block resamples LHC timing by
500MSPS and creates bunch and turn clock vector masks. Those store the
information about both clocks rising edge phase. The 14-bit data from ADC are
left aligned to 16-bit values. The tagger sets their two LSBs to one, when the
ADC sample falls into the edge range. \\
The ADC provides four frames of four 16-bit samples every \SI{8}{\nano s} each
belonging to one ADC channel. The tag can appear in any of the four values. The
system stores data from region of interest, using FIFO. The synchronizer counts
4 turns and then generates a trigger for FIFO. Stored data are then processed as
a stream of values passed to the integrator. This starts summing up values,
when it hits the tag in the data marking the start of the bunch. It creates 64
values offseted by the user when needed. This correct the baseline. The values
are then sent to the exponential moving averager. The result is then stored in
the block ram available on to read from VME64x bus.

\subsection{Installation in LHC}
The instrument front and Acquistion system is located in Point 4 near RF
system. The new installation is shown in Fig. \ref{fig:installation}
highlighted with violet frame. On its right side is the currently working AGM
and on the left side is the BSRS. All the instruments share the same light
source with the BSRT. 
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{installation.jpg}
    \caption{installation picture}
    \label{fig:installation}
\end{figure}
The beam input is demonstrated by the yellow line. It shows beam arriving to
the MCP-PMT. On top of the reflective foil directing light towards the MCP-PMT
is a LED simulating the light source. This helps verifying the system
operation. The AGM amplifier is placed on top of the optical front-end to be
reachable in case of intervention. For reducing the light intensity, there are
pneumatically controlled optical filters in front of the PMT.

\section{Control Interface}
The gateware outputs data from four different block rams. The first stores raw
data from the ADC, that is used correctly set the initial delay of the
instrument's timing. It stores 1.5 turns and therefore it is published with
\SI{3.3}{Hz}. The next two memories store the actual snapshot data and averaged
data, but with finer granularity. They store 10 samples per \SI{10}{ms} window,
which gives the sample rate of \SI{100}{Hz}. The last memory is just bare
averaged data taken every \SI{10}{ms} defining the publishing rate. The
fetching handles the FESA server, which obtains interrupt every time the data
are ready. 
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{control_interface.jpg}
    \caption{installation picture}
    \label{fig:control_interface}
\end{figure}
To simplify the setup tunining a new interface had to be created. It runs as
client of FESA server and displays the content of all the block rams. The main
control panel is depicted in Fig. \ref{fig:control_interface}. It displays
three plots, raw data from the ADC (top plot), processed averaged data (down
plot on the left) and and evolution of the data in time (down plot on the
right). The menu on the left controls the amplifier and bottom menu controls
the acquisition delays and optical filters.

\section{First acquired plots}
First measurements were taken in November 2023 on the ion beam. The
optical system splits the SL in ratio 1:8, so the new system gets
significantly less light then current one. In other word, we expect
lower value deviation for system measuring light with higher intensity.  
\begin{figure}[!htb]
    \begin{center}
        \scalebox{0.54}{\input{plots/ions.pgf}}
        \caption{Comparison of AGMs}
        \label{fig:comparison_chart}
    \end{center}
\end{figure}
The Fig. \ref{fig:comparison_chart} shows first acquisition of the new system
in comparison with the current one. The red plot is measured by the current
system and the blue chart is the new acquisition. In a range from 47th - 63th
bin, the gate is already close. There is just white noise, but the red plot
slowly decays and it continues below the zero line. This artefact is caused by
analog integrators and it is non-linear. The new system removes this effect.
The value deviation of the new acqusition from the current system represents
the yellow plot.   The relative value deviation of the new system from the
current one is depicted with the yellow plot. In this measurement the maximum
deviation is 4\% in the area of the decay of the red plot. The the deviation of
2\% in the steep parts can be caused by the sample phase alignment of the two
systems.

>>>>

\section{System architecture}
The system comprises three main parts. The first part is the optical front-end
(OF), which includes a preamplifier positioned beneath the vacuum chamber. The
second part is a data acquisition system (DAQ) deployed on an FPGA platform
located outside the radiation area. The third part involves software (SW) that
retrieves, interprets, and presents the measured data, facilitating interaction
with the instrument. The system architecture is illustrated in
Fig.~\ref{fig:bsra_chain}, with each part labeled accordingly.
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{bsra_chain.pdf}
    \caption{BSRA Chain}
    \label{fig:bsra_chain}
\end{figure} 
The diagram on the left depicts the layout of the LHC, with beam 1 represented
in red and beam 2 in blue. It includes all four experiments (Alice, Atlas,
LHCb, and CMS). The AGM is situated at Point 4 (indicated by the yellow
square), close to the CMS experiment. The Timing, Trigger, and Control system
(TTC) is shown as a purple rectangle in the center of the LHC ring. This system
receives RF clocking and broadcasts it as messages on the network (TTC
distribution)~\cite{ttc_distribution}. The AGM extracts bunch clock information
(corresponding to the position of bunches) and turn clock information (marking
the start of a turn) from these messages.\\
Beam intensity is gathered by measuring the synchrotron light (SL), as
indicated by the red line directed towards the Multi-channel photomultiplier
(MCP-PMT) in the optical front-end (OF). The beam travers first optical
filters, which increase system dynamic range. Subsequently, the signal is
transmitted over a \SI{100}{m} cable. To compensate for losses in the cable,
the signal is amplified beforehand. It then proceeds to the Data Acquisition
(DAQ) system, which measures \SI{6.4}{\micro\second} window and integrates the
intervals of \SI{100}{\nano\second}. This creates set of 64 values published to
the SW every \SI{10}{\micro\second}.

\subsection{Working principle}
The measurement period is determined by the MCP-PMT used, which is the gated
HAMAMATSU R5916U-50 with a duty cycle of \SI{1}{\%}. With a gate pulse duration
of \SI{3}{\micro\second} and one turn cycle length of \SI{89}{\micro\second},
measurements are taken every 4th clock cycle (\SI{356}{\micro\second}),
reducing the duty cycle to \SI{0.84}{\%}.\\
The system captures 64 values with a granularity of \SI{100}{\nano\second}. The
MCP-PMT gate duration is \SI{3}{\micro\second} providing an additional degree of
freedom in system control. Each \SI{100}{\nano\second} value is averaged in an
extra EMA and provided to the software every \SI{100}{\micro\second}. This
time is enough to react to changes in AG. The population can change from
\SI{1.6}{\second} to \SI{25}{\second} due to different
effects~\cite{high_sensitivity_measurement}.

\subsection{Current Solution}
The current solution uses DAB64x card deploying FPGA Altera Stratix EP1S40. The
platform has two FMC connectors. There are mounted two IBMS module. Those
modules integrate voltage on input using ASIC lhcb2002b~\cite{lhcb_asic}.
To get the maximal resolution of the ADC, the signal is amplified by HAMAMATSU
C5594 with static gain \SI{36}{dBV}, bandwith \SI{1.5}{GHz} and the low cutoff
frequency 50kHz.
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{existing_system_processing.pdf}
    \caption{Current system block diagram}
    \label{fig:current_system_processing}
\end{figure}
The system schematic is in Fig.~\ref{fig:current_system_processing}. The OF is
the same as described in the system architecture chapter. The picture omits the
filters, because they are used in all cases. The MCP-PMT signal needs to be
amplified by at least 34dB to use the full scale of the 40Mhz ADC. The
Hamamatsu C559 is used~\cite{bsra_first_operation}. The signal belonging
to one bunch (\SI{25}{ns}) is integrated in the IBMS (blue triangle with a
capacitor in the feedback) sampled by ADC (violet rectangle in the figure). The
DAQ integrates 4 samples (light blue rectangle with $\sum$ symbol) to calculate
charge in \SI{100}{ns} interval. It produces 64 values, from which are created
two sets of 64 values with the standard deviation and the mean value is
calculated. Both sets are passed to the EMA block (green rectangle in
the figure). All data are saved in the block ram. This is is than shared with
the PC over wishbone to VME64 bridge. The PC runs server which provides the
FESA interface to the connected clients.

\subsection{Constraints and Limitations}
The current AGM returns artefacts in the measurements. The signal, which lays
outside of the gate is not reflecting behaviour of white noise. This is caused
by the lhcb2002b ASIC. The integrators gain is not linear, have different
offset and dead times. This means, that system needs to correct at each
integrator these effects, which creates uncertainties in the results. This
results in complicated calibration procedur.\\
The system uses old FPGA platform for which development sofware tools are not
compatible with newest operation systems. The amplifier is not variable, which
results in lower resolution for smaller magnitudes.

\section{System Upgrade}
To resolve the issue of the maintenance, the VFC-HD carrier is used with
additional RTM board providing driver for the gate and control of the built-in
test LED. The same carrier board with 500MSPS 14-bit ADC has been used in other
projects and so it provided the requirement for reducing the maintenance efford.
The new system removes IBMS cards with lhcb2002b integrators and moving the
whole integration process to the gateware.

\subsection{Low band Amplifier}
The new custom amplififer is designed to allow work with higher signal dynamic
range, because of its variability.  
% A = U^2/(i^2 * R^2) => A_dB = 20*log10(U/(i*R))
In the Fig. \ref{fig:amp_schematics} is shown amplifier's block scheme. All the
settings is controlled via UART interface. It provides changing the variable
current-to-voltage conversion factor from \SI{5.8}{mV/\micro A} -
\SI{1.1}{V/\micro A}. This corresponds to the Voltage gain from \SI{41}{dB} to
\SI{87}{dB}. The AGM ADC has a no zero offset, so the signal can be shifted in the
amplifier before post-processing.\\
The amplifier features also alarm signal generator. This serves to turn of the
gate, when the light impinging is to intense and it could damage the
multi-channel plate inside the PMT. The alarm signal is send to the gateware,
where it is handled. The alarm feature has a variable threshold set.   
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{amp_schematics.pdf}
    \caption{New AGM custom amplifier}
    \label{fig:amp_schematics}
\end{figure}
The amplifier design has three switches. First switch can set pre-integrator,
to filter out spikes caused by dark counts of the PMT. Second switch can
activate either manual or gate driven integration of the acquisition window.  
Last switch activates low pass filtering with cutoff frequency of 40MHz.

\subsection{Acquisition system}
The DAQ had to be redesigned to be compatible with the new VFC-HD carrier. It
needed Rear transition module (RTM) to control the gate and built-in test LED.  
The Fig.~\ref{fig:bsra_daq} is depicted DAQ functionality principle. 
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{bsra_daq.pdf}
    \caption{Ackquisition system schematics}
    \label{fig:bsra_daq}
\end{figure}
The new DAQ gets asynchronous data samples from ADC 500MSPS 14-bit (violet
rectangle) in the block of 4 frames every \SI{8}{\nano s} belonging to one
channel. Each frame has 4 x \SI{16}{bit} values. To calculate the integrals of
\SI{100}{\nano\second}, the system tags the data. The tagging block resamples
LHC timing by 500MSPS and creates bunch and turn clock vector masks. Those
store the information about both clocks phases. The 14-bit data from ADC are
left aligned to 16-bit values. The tagger sets their two LSBs to one, when the
ADC sample falls into the edge range. The system stores data from region of
interest, into the FIFO using the synchronization block pulse. Stored data are
then processed as a stream of values passed to the integrator. This starts
summing up values, when it hits the tag in the data indicating the start of the
bunch. It creates 64 values offseted from the pedestal memory (P[63:0]). This
subtracts accumulated charge at the gate opening and closing edge. The values
are then sent to the EMA and the result stored in the block ram available on
the VME64x bus. The format of the data provided to the PC with runnig FESA
server is the same with the current AGM~\cite{my_thesis}.

\subsection{Installation in LHC}
The instrument front and Acquistion system is located in LHC Point 4 near RF
system. The new installation is shown in Fig.~\ref{fig:installation}
highlighted with violet frame. On its right side is the currently used AGM
and on the left side is the BSRS. All the instruments share the same light
source with the BSRT. The instrument is pulled out from the shielding and the
red arrow ilustrates, where the light comes from and goes in to the MCP-PMT of
the new AGM.
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{installation.jpg}
    \caption{New AGM installed in Point 4 next to BSRT}
    \label{fig:installation}
\end{figure}
On top of the reflective foil directing light towards the MCP-PMT
is a LED simulating the light source. This helps verifying the system
operation. The AGM amplifier is placed on top of the optical front-end to be
reachable in case of intervention. For reducing the light intensity, there are
pneumatically controlled optical filters in front of the MCP-PMT.

\section{Control Interface}
The gateware outputs data from four different block rams. The first stores raw
data from the ADC, that is used correctly set the initial delay of the
instrument's timing. It stores 1.5 turns and therefore it is published with
\SI{3.3}{Hz}. The next two memories store the actual snapshot data and averaged
data, but with finer granularity. They store 10 samples per \SI{10}{ms} window,
which gives the sample rate of \SI{100}{Hz}. The last memory is just bare
averaged data taken every \SI{10}{ms} defining the publishing rate. The
fetching handles the FESA server, which obtains interrupt every time the data
are ready. 
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{control_interface.jpg}
    \caption{New AGM expert graphical interface}
    \label{fig:control_interface}
\end{figure}
To simplify the setup tunining a new interface had to be created. It runs as
client of FESA server and displays the content of all the block rams. The main
control panel is depicted in Fig. \ref{fig:control_interface}. It displays
three plots, raw data from the ADC (top plot), processed averaged data (down
plot on the left) and and evolution of the data in time (down plot on the
right). The menu on the left controls the amplifier and bottom menu controls
the acquisition delays and optical filters.

\section{First acquired plots}
First measurements were taken in November 2023 on the ion beam. The
optical system splits the SL in ratio 1:8, so the new system gets
significantly less light then current one. In other word, we expect
lower value deviation for system measuring light with higher intensity.  
\begin{figure}[!htb]
    \begin{center}
        \scalebox{0.54}{\input{plots/ions.pgf}}
        \caption{Features comparison of AGMs}
        \label{fig:comparison_chart}
    \end{center}
\end{figure}
The Fig. \ref{fig:comparison_chart} shows first acquisition of the new system
in comparison with the current one. The red plot is measured by the current
system and the blue chart is the new acquisition. In a range from 47th - 63th
bin, the gate is already close. There is just white noise, but the red plot
slowly decays and it continues below the zero line. This artefact is caused by
analog integrators and it is non-linear. The new system removes this effect.
The value deviation of the new acqusition from the current system represents
the yellow plot.   The relative value deviation of the new system from the
current one is depicted with the yellow plot. In this measurement the maximum
deviation is 4\% in the area of the decay of the red plot. The the deviation of
2\% in the steep parts can be caused by the sample phase alignment of the two
systems.
